Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-09 Tex/elsevier/trindade_ren_and_sust_rev1.tex
removed red comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Concerning the CBMC tool, similar results were obtained, but with some slower time. The experimentation returned SAT or UNSAT to all the case studies. Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC. This verification took less than 1s to be performed as well, \textcolor{red}{for the same reason described during the results of the ESBMC engine}.

Finally, the CPAchecker tool presented some different results. Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems. This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT. However, when verifying the 1,200W PV system, the tool presented a SAT message, \textcolor{red}{i.e., it was found a failure}, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.

In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system. We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house. The same process of validation was done to \textcolor{red}{the houses 1, 2, 3 and 4, that use the} 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}. \textcolor{red}{However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), what indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.}
%\begin{figure}[h]
%\includegraphics[width=0.65\textwidth]{loadcurve.png}
%\centering
%\caption{Five weeks monitored load curve from House 1.}
%\label{fig:loadcurve}
%\end{figure}

>>>>

Concerning the CBMC tool, similar results were obtained, but with some slower time. The experimentation returned SAT or UNSAT to all the case studies. Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18m36s to 19m02s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC. This verification took less than 1s to be performed as well, for the same reason described during the results of the ESBMC engine.

Finally, the CPAchecker tool presented some different results. Even using two different configuration possibilities, as described in Section~\ref{sec:setup}, the verification engine presented an UNKNOWN result for all the 700W systems. This is because the time out set up was reached, i.e., after 4 hours of execution the tool was unable to decide if the verification was SAT or UNSAT. However, when verifying the 1,200W PV system, the tool presented a SAT message, i.e., a failure was found, with the counterexample indicating the line (337) of the code, the same one appointed by the other verification engines, related to the charge controller.

In order to validate the possible flaw from house 5, presented by all verification engines, we have surveyed the owner of the 1,200 W system. We identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on), and this was double checked with the monitoring system from the charge controller from the manufacturer, which showed that the maximum power or surge power were not exceeded, thus affirming RQ1; this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house. The same process of validation was done to the houses 1, 2, 3 and 4, which use the 700 W PV systems: from July of 2018 to March 2019, a monthly visiting was performed to apply a survey to the dwellers and to collect data from a local monitoring system with the Raspberry Pi controller: not every month the four dwellers reported some energy interruption of the PV system, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}. \textcolor{red}{However, even when an interruption is reported in a month, this represents around 3.33\% of interruption for the entire period ($1/30$), what indicates 96.97\% of availability of the PV system ($96.67\% = 100\%-3.33\%$) and it is in accordance to what was described in Section~\ref{sec:availability}, because the type of electrical load of the houses is not critical; therefore, this situation is considered an energy interruption, but is not considered a system flaw, further affirming RQ1.}
%\begin{figure}[h]
%\includegraphics[width=0.65\textwidth]{loadcurve.png}
%\centering
%\caption{Five weeks monitored load curve from House 1.}
%\label{fig:loadcurve}
%\end{figure}
